Research Review: \\The Extent of Adaptive Wild Introgression in Crops

### 2018-08-02 paper.tex

Measurement of the strength of the initial domestication bottleneck may also be impacted by adaptive introgression during the spread of crops.
Crop wild relatives have distinct demographies when compared to domesticates and may therefore have contrasting effective population sizes ($N_e$).
The influence of wild relative introgression on estimates of the domestication bottleneck will depend on a number of factors including the magnitude of gene flow, the $N_e$ of the introgressing taxon, and the strength of selection on haplotypes following introgression.
For example, substantial introgression from a wild taxon with a historically higher $N_e$ will lead to underestimates of the overall strength of the initial domestication bottleneck.

>>>>

Measurement of the strength of the initial domestication bottleneck may also be impacted by adaptive introgression during the spread of crops.
Crop wild relatives have distinct demographies when compared to domesticates and may therefore have contrasting effective population sizes ($N_e$).
Due to the domestication bottleneck, domesticated organisms typically have lower $N_e$, less effective genome-wide selection, and therefore higher genetic load, compared to their wild relatives, a pattern known as the "cost of domestication" \cite{moyers2017genetic}.
The influence of wild relative introgression on estimates of the domestication bottleneck will depend on a number of factors including the magnitude of gene flow, the $N_e$ of the introgressing taxon, and the strength of selection on haplotypes following introgression.
For example, substantial introgression from a wild taxon with a historically higher $N_e$ will lead to underestimates of the overall strength of the initial domestication bottleneck.

Depending on the $N_e$ of wild species relative to the domesticate, introgression into the domesticate can either ameliorate or exascerbate the prevalence of deleterious alleles.
Many crops show evidence of genetic load, including maize \cite{wang2017interplay}, cassava \cite{ramu2017cassava}, and grape \cite{zhou2017evolutionary}.
For this reason, introgression from high-$N_e$ wild relatives is more likely to reduce load.
In accord with these predictions, Li et al. \cite{wang2017interplay} found that $N_e$ of maize dropped due to the domestication bottleneck, but that highland maize from Mexico, Guatemala, and the southwestern United States which maintained mexicana introgressions subsequently had fewer deleterious alleles.
